### 2019-06-08 doc/chapters/introduction.tex
added title
changed from foot note to href

Stainless supports only a subset of Scala.
They call is Pure Scala.
You can find the specification of Pure Scala on the Stainless website\footnote{\url{https://epfl-lara.github.io/stainless/purescala.html}}.

In addition, Stainless has its own library with annotations, reimplementaion of some core data types, collections and input-output functions and more.
Some of them are described on the website\footnote{\url{https://epfl-lara.github.io/stainless/library.html}}.
There are more details about library in the source code of Stainless on GitHub in the folder \textit{frontends/library/stainless}\footnote{\url{https://github.com/epfl-lara/stainless}}.

@@

In the work we verify some fragments of the code of Bitcoin-S.
Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S.
Protocol data structures are defined in the package \textbf{bitcoin-s-core}.
This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is an RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
The whole list of packages can be found on GitHub\footnote{\url{https://github.com/bitcoin-s}}.

@@

>>>>

Stainless supports only a subset of Scala.
They call is Pure Scala.
You can find the specification of Pure Scala on the Stainless website in the section \href{https://epfl-lara.github.io/stainless/purescala.html}{Pure Scala}.

In addition, Stainless has its own library with annotations, reimplementaion of some core data types, collections and input-output functions and more.
Some of them are described on the website in the section \href{https://epfl-lara.github.io/stainless/library.html}{Stainless Library}.
There are more details about library in the source code of Stainless on GitHub in the folder \href{https://github.com/epfl-lara/stainless}{\textit{frontends/library/stainless}}.

@@

In the work we verify some fragments of the code of Bitcoin-S.
Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S.
Protocol data structures are defined in the package \textbf{bitcoin-s-core}.
This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is an RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
The whole list of packages can be found on GitHub in the \href{https://github.com/bitcoin-s}{organization Bitcoin-S}.

@@

\section{The Properties to Verify}

### 2019-06-08 doc/chapters/towards_verifying_addition.tex
changed from foot note to href

This is, due to the internal design of Scala and Java.
It's possible to reason about case object but not about object.
This needs a fundamental knowledge of Scala and some functional paradigms that should not be part of this thesis.
The issue \mypound520 on Stainless GitHub\footnote{\url{https://github.com/epfl-lara/stainless/issues/520}} gives some thoughts if you want to know more.

@@

This is a missing feature in Stainless.
It does not support upper type bound on the class itself.
To track this, there is the issue \mypound519 on GitHub\footnote{\url{https://github.com/epfl-lara/stainless/issues/519}}.
\begin{lstlisting}[language=scala]
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

@@

This was a missing feature of Stainless that was fixed on Mai 28, 2019 with pull request \mypound470 on GitHub\footnote{\url{https://github.com/epfl-lara/stainless/pull/470}}.
Now it should work without this change.

>>>>

This is, due to the internal design of Scala and Java.
It's possible to reason about case object but not about object.
This needs a fundamental knowledge of Scala and some functional paradigms that should not be part of this thesis.
The \href{https://github.com/epfl-lara/stainless/issues/520}{issue \mypound520} on Stainless GitHub gives some thoughts if you want to know more.

@@

This is a missing feature in Stainless.
It does not support upper type bound on the class itself.
To track this, there is the \href{https://github.com/epfl-lara/stainless/issues/519}{issue \mypound519} on GitHub.
\begin{lstlisting}[language=scala]
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

@@

This was a missing feature of Stainless that was fixed on Mai 28, 2019 with \href{https://github.com/epfl-lara/stainless/pull/470}{pull request \mypound470} on GitHub.
Now it should work without this change.

### 2019-06-08 doc/chapters/trying_verify_checktx.tex
changed from foot note to href

This was fixed in pull request \mypound435 on GitHub\footnote{\url{https://github.com/bitcoin-s/bitcoin-s/pull/435}} at April 23, 2019 by us along a unit test to prevent this bug from appearing again in the future.

>>>>

This was fixed in \href{https://github.com/bitcoin-s/bitcoin-s/pull/435}{pull request \mypound435} on GitHub at April 23, 2019 by us along a unit test to prevent this bug from appearing again in the future.
